### 2022-04-18 README.Rmd
update initial data to 2020

# bicla-R

@@

The goal of bicla-R is to store code and (in the releases) data for estimating cycling potential and influencing policy.

@@

- TRIPS_original.Rds, the original OD dataset

>>>>

# biclar

@@

The goal of biclar is to store code and (in the releases) data for estimating cycling potential and influencing policy.

@@

- [CAOP 2020](https://www.dgterritorio.gov.pt/cartografia/cartografia-tematica/caop?language=en) - Official limits of Portuguese areas.
- TRIPS_original.Rds, the original OD dataset, from INE (2018)
